---
title: "A stargazer cheatsheet"
author: "Jake Russ"
date: "Monday, August 18, 2014"
output: 
  html_document:
    theme: spacelab
    keep_md: true
    toc: true
    highlight: haddock
---





## Dataset: dplyr and nycflights13

Setting up a dataset for this cheatsheet allows me to spotlight two recent
R packages created by [Hadley Wickham](http://had.co.nz/). The first, 
[dplyr](https://github.com/hadley/dplyr), is a set of new tools for data 
manipulation. Using `dplyr`, I will extract flights and weather data from 
another new package called 
[nycflights13](https://github.com/hadley/nycflights13). With this data I 
will show how to estimate a couple of regression models and nicely format the 
results into tables with `stargazer`.

```{r, echo = TRUE, warning = FALSE, message = FALSE}
library(dplyr)
library(nycflights13)

library("AER") ## Applied Econometrics with R 

daily <- flights %>%
  filter(origin == "EWR") %>%
  group_by(year, month, day) %>%
  summarise(delay = mean(dep_delay, na.rm = TRUE))

daily_weather <- weather %>%
  filter(origin == "EWR") %>%
  group_by(year, month, day) %>%
  summarise(temp   = mean(temp, na.rm = TRUE),
            wind   = mean(wind_speed, na.rm = TRUE),
            precip = sum(precip, na.rm = TRUE))

both <- inner_join(daily, daily_weather)

## Create an indicator for quarter
both$quarter <- cut(both$month, breaks = c(0, 3, 6, 9, 12), 
                                labels = c("1", "2", "3", "4"))

## Create a vector of class logical
both$hot <- as.logical(both$temp > 85)

head(both)

```

We can use the `both` data frame to estimate a couple of linear models 
predicting the average delay out of Newark controlling for the weather. The 
first model will use only the weather variables and in the second I'll add 
dummy variables indicating the quarter. The raw R output:

```{r, echo = TRUE}
output  <- lm(delay ~ temp + wind + precip, data = both)
output2 <- lm(delay ~ temp + wind + precip + quarter, data = both)

## Instrumental variables model 
output3 <- ivreg(delay ~ temp + wind + precip| . - temp + hot, data = both)

summary(output)
summary(output2)

```

\
[Back to table of contents](#TOC)

## Quick note

Since I'm using [knitr](http://cran.rstudio.com/web/packages/knitr/index.html) 
and [R markdown](http://rmarkdown.rstudio.com/) to create this webpage, in the 
code that follows I will include the `stargazer` option `type = "html"`. 
`stargazer` is set to produce **LaTeX** output by default. If you desire 
**LaTeX** output, just remove the type option from the code below.

```{r, warning = FALSE, message = FALSE}
library(stargazer)
```

\
[Back to table of contents](#TOC)

## The default summary statistics table
```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(both, type = "html")
```
  
When supplied a data frame, by default `stargazer` creates a table with summary 
statistics. If the `summary` option is set to `FALSE` then stargazer 
will instead print the contents of the data frame.

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
## Use only a few rows
both2 <- both[1:6, ]

stargazer(both2, type = "html", summary = FALSE)
```


### Change which statistics are displayed

In order to customize which summary statistics are displayed, change any of the
the following (logical) parameters, `nobs`, `mean.sd`, `min.max`, `median`, and
`iqr`. 

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(both, type = "html", nobs = FALSE, mean.sd = TRUE, median = TRUE,
          iqr = TRUE)
```

### Change which statistics are displayed (a second way)

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(both, type = "html", summary.stat = c("n", "p75", "sd"))
```

### Remove logical variables in the summary statistics

`stargazer` reports summary statistics for logical variables by default 
(0 = FALSE and 1 = TRUE). To supress the reporting of logical vectors change 
`summary.logical` to `FALSE`. Note the stats for our vector `hot` are gone. 

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(both, type = "html", summary.logical = FALSE)
```

\
[Back to table of contents](#TOC)

## The default regression table

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output2, type = "html")
```

\
[Back to table of contents](#TOC)

## Change the style

`stargazer` includes several pre-formatted styles that imitate popular
academic journals. Simply change the `style` parameter.

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output2, type = "html", style = "qje")
```

\
[Back to table of contents](#TOC)

## Labelling the table

### Add a title; change the variable labels 

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output2, type = "html", 
          title            = "These are awesome results!",
          covariate.labels = c("Temperature", "Wind speed", "Rain (inches)",
                               "2nd quarter", "3rd quarter", "Fourth quarter"),
          dep.var.caption  = "A better caption",
          dep.var.labels   = "Flight delay (in minutes)")
```

### Exclude the dependent variable label or the model numbers

Note the dependent variable caption stays. To additionally remove the caption 
add `dep.var.caption = ""`.

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output2, type = "html", 
          dep.var.labels.include = FALSE,
          model.numbers          = FALSE)
```

### Change the column names

To change the column names just supply a character vector with the new labels, 
as shown below. 

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output2, type = "html", column.labels = c("Good", "Better"))
```

### Apply a label to more than one column

The option `column.separate` allows for assigning a label to more than one 
column. In this example I told `stargazer` to report each regression twice, for a
total of four columns. Using `column.separate`, `stargazer` now applies the first
label to the first two columns and the second label to the next two columns.

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output, output2, output2, type = "html", 
          column.labels   = c("Good", "Better"),
          column.separate = c(2, 2))
```

### Model names

When the results from different types of regression models (e.g., "OLS", 
"probit") are displayed in the same table `stargazer` adds a row indicating 
model type. Remove these labels by including `model.names = FALSE` (not shown).

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output3, type = "html")
```

\
[Back to table of contents](#TOC)

## Change the default output

### Standard errors, t-statistics, or p-values?

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output2, type = "html", 
          column.labels = c("Good", "Better"))
```

### 

\
[Back to table of contents](#TOC)

## Omit parts of the default output

In fixed effect model specifications it is often undesirable to report the 
fixed effect coefficients. To omit any coefficient, supply a regular 
expression to `omit`.

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output2, type = "html", omit = "quarter")
```

### Reporting omitted variables

Add the `omit.labels` parameter to report which variables have been omitted. 
Must be the same length as the number of regular expressions supplied to `omit`.
By default `omit.labels` reports "Yes" or "No". To change this supply 
a new vector of length 2 to `omit.yes.no = c("Yes", "No")`.

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
stargazer(output, output2, type = "html", 
          omit        = "quarter",
          omit.labels = "Quarter dummies?")
```

### Omit parts of the regression output

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
## Remove r-square and f-statistic
stargazer(output, output2, type = "html", 
          omit.stat = c("rsq", "f"))
```

### Omit whole parts of the table

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
## Remove statistics and notes sections completely
stargazer(output, output2, type = "html", 
          omit.table.layout = "sn")
```

\
[Back to table of contents](#TOC)


## Statistical significance options

By default `stargazer` uses \*\*\*, \*\*, and \* to denote statistical 
significance at the one, five, and ten percent levels. This behavior can be 
changed by altering the `star.char` option. 

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
## Remove statistics and notes sections completely
stargazer(output, output2, type = "html", 
          star.char = c("@", "@@", "@@@"))
```

### Change the cutoffs for significance

Notice that temperature, quarter3, and quarter4 have each lost a gold star 
because we made it tougher to earn them.

```{r, echo = TRUE, warning = FALSE, message = FALSE, results='asis'}
## Remove statistics and notes sections completely
stargazer(output, output2, type = "html", 
          star.cutoffs = c(0.05, 0.01, 0.001)) # star.cutoffs = NULL by default
```

\
[Back to table of contents](#TOC)







